An Embedding Framework for Consistent Polyhedral Surrogates

### 2022-05-24 poly-embed-journal/poly-embed-journal.tex
proof of prop and cor in Section 4

\paragraph{Remarks.}
Construction~\ref{const:eps-thick-link} is not necessarily computationally efficient as the number of labels $n$ grows.
In practice this potential inefficiency is not typically a concern, as the family of losses typically has some closed form expression in terms of $n$, and thus the construction can proceed at the symbolic level.
We illustrate this formulaic approach in \S~\ref{sec:abstain}.

Applying the $\epsilon$-thickened link construction additionally enables one to verify the consistency of a proposed link $\psi^*$.
For a given $\epsilon$ and norm $\|\cdot\|$, suppose one follows the routine of Construction~\ref{const:eps-thick-link} until the last step in which values for the link $\psi$ are selected.
Instead, we can simply test whether the proposed link values are contained in the valid choices, i.e., if $\psi^*(u) \in \Psi(u)$ for all $u\in\reals^d$.
If so, then the proposed link $\psi^*$ is calibrated.
See \S~\ref{sec:top-k} for an illustration of this test.

\botodo{Should we comment on computing the $\epsilon$?}
\raft{Don't recall what we have to say... but this would be a great spot to do so.  Or at least make the point that the regret bounds (below) get better the higher $\epsilon$ is.}

\paragraph{A converse to Theorem \ref{thm:thickened-separated}.}
\raf{Started but did not finish; in particular, did not prove the proposition.  I'd suggest taking the last paragraph of the proof of Theorem~\ref{thm:thickened-separated} and making that one direction of the proof of this proposition, and then using the proposition to prove the theorem.}
Perhaps surprisingly, one can also show that \emph{every} calibrated link from a polyhedral surrogate to a discrete loss is produced by Construction \ref{const:eps-thick-link}.
This result follows from the fact, stated now, that Construction~\ref{const:eps-thick-link} with $\|\cdot\|_\infty$ is exactly enforcing $\epsilon$-separation; from Theorem~\ref{thm:calibrated-separated}, every calibrated link is therefore yielded by the construction for some sufficiently small $\epsilon$.

\begin{proposition}
  Let polyhedral surrogate $L:\reals^d \to \reals^\Y_+$ and discrete loss $\ell:\R\to\reals^\Y_+$ be given.
  Let $\epsilon>0$ be given, and let $\Psi$ be the link envelope from Construction~\ref{const:eps-thick-link} for $\epsilon$ and $\|\cdot\|_\infty$.
  Then $\psi$ is $\epsilon$-separated if and only if $\psi(u) \in \Psi(u)$ for all $u\in\reals^d$.
\end{proposition}

>>>>

\paragraph{A converse to Theorem \ref{thm:thickened-separated}.}
\raft{I'd suggest taking the last paragraph of the proof of Theorem~\ref{thm:thickened-separated} and making that one direction of the proof of this proposition, and then using the proposition to prove the theorem. \bo{didn't do this, for now at least}}
Perhaps surprisingly, one can also show that \emph{every} calibrated link from a polyhedral surrogate to a discrete loss is produced by Construction \ref{const:eps-thick-link}.
This result follows from the fact, stated now, that Construction~\ref{const:eps-thick-link} with $\|\cdot\|_\infty$ is exactly enforcing $\epsilon$-separation; from Theorem~\ref{thm:calibrated-separated}, every calibrated link is therefore yielded by the construction for some sufficiently small $\epsilon$.

\begin{proposition}
  Let polyhedral surrogate $L:\reals^d \to \reals^\Y_+$ and discrete loss $\ell:\R\to\reals^\Y_+$ be given.
  Let $\epsilon>0$ be given, and let $\Psi$ be the link envelope from Construction~\ref{const:eps-thick-link} for $\epsilon$ and $\|\cdot\|_\infty$.
  Then $\psi$ is $\epsilon$-separated if and only if $\psi(u) \in \Psi(u)$ for all $u\in\reals^d$.
\end{proposition}
\begin{proof}
  For $u\in\reals^d$, let $P_u$ consist of all $p\in\simplex$ such that $d_{\infty}(u,\Gamma(p)) < \epsilon$.
  If and only if $\psi$ is $\epsilon$-separated, then for all $u$, $\psi(u) \in \cap_{p \in P_u} \gamma(p)$.
  Meanwhile by definition, $\Psi(u) = \cap_{p \in P_u} R_p$ where $R_p = \{r \in \R ~:~ \phi(r) \in \Gamma(p)\}$, the set of reports that embed into $\Gamma(p)$.
  By definition of embedding, $R_p = \gamma(p)$, completing the proof. \botodo{Ok?}
\end{proof}

\begin{corollary}
  A link $\psi$ is calibrated for a given discrete target $\ell$ and polyhedral surrogate $L$ if and only if there exists $\epsilon$ such that $\psi$ is produced by Construction \ref{const:eps-thick-link}$(L,\ell,\epsilon,\|\cdot\|_{\infty})$.
\end{corollary}

\paragraph{Remarks.}
Applying Construction \ref{const:eps-thick-link} enables one to verify the consistency of a proposed link $\psi^*$.
For a given $\epsilon$ and norm $\|\cdot\|$, suppose one follows the routine of Construction~\ref{const:eps-thick-link} until the last step in which values for the link $\psi$ are selected.
Instead, we can simply test whether the proposed link values are contained in the valid choices, i.e., if $\psi^*(u) \in \Psi(u)$ for all $u\in\reals^d$.
If so, then the proposed link $\psi^*$ is calibrated.
See \S~\ref{sec:top-k} for an illustration of this test.
On the other hand, if $\psi^*$ cannot possibly be produced from Construction \ref{const:eps-thick-link}, then it cannot be a calibrated link.
This can be shown, for example, if there exists a point $u$ where $\Psi(u)$ is empty for all $\epsilon > 0$.\botodo{Is this a reasonable possibility?}

Construction~\ref{const:eps-thick-link} is not necessarily computationally efficient as the number of labels $n$ grows.
In practice this potential inefficiency is not typically a concern, as the family of losses typically has some closed form expression in terms of $n$, and thus the construction can proceed at the symbolic level.
We illustrate this formulaic approach in \S~\ref{sec:abstain}.

\botodo{Should we comment on computing the $\epsilon$?}
\raft{Don't recall what we have to say... but this would be a great spot to do so.  Or at least make the point that the regret bounds (below) get better the higher $\epsilon$ is.}
\botodo{Not sure if we have anything useful to say}
